Topological Equivariant Artist Model

### 2021-03-22 paper/paper.tex
reworked monoid, q, and xi figures

%other entries to be set up for journal
\shortauthortitle{ \MakeLowercase{\textit{et al.}}: Topological Equivariant Artist Model}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

@@

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
% http://ieeevis.org/year/2021/info/call-participation/paper-keywords
\keywords{Taxonomy, Models, Frameworks, Theory }

@@

\autoref{fig:math:artist:nu} illustrates a \vchannel\ that preserves partial order relations because 
ou would have to state that the monoid of monitonic actions is equivalent to the partial order realationship
ok
so that the order is preserved IF and only IF it is an equivariant map.
I think that is true but it would be nice to have a reference.
but then you don't have to really plot out m.

Generally, for the Steven's scales\cite{stevensTheoryScalesMeasurement1946} an equivariant \vchannel\ has the following properties
\begin{table}[H]
  \begin{tabulary}{\columnwidth}{llL}
      nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
      ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
      interval &  translation &  $\vchannel (x + c) = \vchannel(x) + c$ \\
      ratio &  scaling &  $\vchannel(xc) = \vchannel(x)*c $\\
  \end{tabulary}
\end{table}
\noindent where the middle column is the group structure. Therefore, a \vchannel\ is equivariant if it satisfies the listed condition.

>>>>

%other entries to be set up for journal
\shortauthortitle{Aizenman \MakeLowercase{\textit{et al.}}: Topological Equivariant Artist Model}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

@@

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
% http://ieeevis.org/year/2021/info/call-participation/paper-keywords
\keywords{Taxonomy, Models, Frameworks, Theory}

@@

\autoref{fig:math:artist:nu} illustrates a \vchannel\ that preserves partial order relations.

Stevens scales\cite{stevensTheoryScalesMeasurement1946} are groups, which are monoids with invertible elements,

\begin{table}[H]
  \begin{tabulary}{\columnwidth}{|llL|}\hline
      \textbf{scale} & \textbf{group} & \textbf{constraint}\\ \hline
      nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
      ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
      interval &  translation &  $\vchannel (x + c) = \vchannel(x) + c$ \\
      ratio &  scaling &  $\vchannel(xc) = \vchannel(x)*c $\\ \hline
  \end{tabulary}
\end{table}

\noindent where the group is a monoid with invertible elements. Therefore, a \vchannel\ is equivariant if it satisfies
